Variable Selection in Convex Function Estimation

### 2013-10-04 tex/scam/appendix.tex
appendix fixed

Suppose that $c s L \lambda_n \rightarrow 0$ and $c L b (B+\sigma)B\sigma \sqrt{\frac{1}{n^{4/5}} s^5 \log sn} \rightarrow 0$.

@@

By Theorem~\ref{thm:uniform_risk_deviation}, we know that under the condition of the theorem, $\tau_n \leq  bLB\sigma(B+\sigma)\sqrt{ \frac{1}{cn^{4/5}} s^5 \log n}$.

@@

For $n$ large enough such that
\[
c s L \lambda_n < \alpha \trm{ and } bLB\sigma(B+\sigma) \sqrt{ \frac{1}{n^{4/5}} s^5 \log sn}) < \alpha
\]
we get that $\hat{R}_s(\hat{f}) + \lambda_n \rho_n(\hat{r}) > \hat{R}_s(f^*_s) + \lambda_n \rho_n(f^*_s)$, which is a contradiction since we assumed that $\hat{f}$ minimizes the regularized empirical risk.

@@

\begin{theorem} (Uniform Risk Deviation)
\label{thm:uniform_risk_deviation}
For all $n > n_0$, we have that, with probability at least $1 - \frac{C}{n}$, 
\[
\sup_{f \in \mathcal{C}^s[b,B,L]} |\hat{R}_s(f) - R_s(f)| \leq B\sigma(B+\sigma)Lb\sqrt{ \frac{1}{cn^{4/5}} s^5 \log sn}
\]
\end{theorem}

@@

The first term, fully expanded, is $\frac{1}{n} \sum_{i=1}^n w_i (f_0(X^{(i)}) - \bar{f}_0 - f'(X^{(i)}))$. Since $w_i$ and $X^{(i)}$ are independent, we use the sub-Gaussian concentration inequality. Note that $|f_0(X^{(i)}) - \bar{f}_0 - f'(X^{(i)})| \leq 3sB$, and so $|\langle w, f_0 - \bar{f}_0 - f' \rangle| > t$ with probability at most $C \exp\big( - c n t^2 \frac{1}{\sigma^2 (sB)^2} \big)$.

@@

$\bar{w} \leq \sigma\frac{1}{cn}$ with probability at least $1-\frac{C}{n}$.

@@

Because $f_0(X^{(i)}) - f'^(X^{(i)})$ is bounded by $2sB$, $\| f_0 - f'\|_n^2$ is the empirical average of $n$ random variables bounded by $9(sB)^2$.

Using Hoeffding Inequality then, we know that the probability $\Big| \| f_0 -\mu - f' \|_n^2 - \E(f_0(X) - f '(X))^2 \Big| \geq t $ is at most $C \exp( - c n t^2 \frac{1}{(sB)^4})$.

Consider now the term $2 \langle w, f_0 - f' \rangle_n \coloneqq \frac{2}{n} \sum_{i=1}^n w_i ( f_0(X^{(i)}) - f'(X^{(i)}))$. We note that $w_i$ and $X^{(i)}$ are independent, $w_i$ is subgaussian.

The $n$-dimensional vector $\{ \frac{1}{n} ( f_0(X^{(i)}) - f'(X^{(i)})) \}_i$ has norm at most $\frac{sB}{\sqrt{n}}$. Therefore, $|2 \langle w, f_0 - f' \rangle_n | \geq t$ with probability at most $C \exp( - c n t^2 \frac{1}{\sigma^2(sB)^2})$.

The last term $\| w \|_n^2 = \frac{1}{n} \sum_{i=1}^n w_i^2$. Using subexponential concentration, we know that $ |\| w \|_n^2 - \E|w|^2 | \geq t$ occurs with probability at most $C \exp( - c n \frac{1}{\sigma^2} )$ for $n$ larger than some $n_0$.

and applying union bound, we have that $\sup_{f' \in \mathcal{C}_\epsilon[s,b,B,L]} | \hat{R}_s(f') - R_s(f') | \geq t$ occurs with probability at most
\[
C \exp\big( s\left( \frac{bBLs}{\epsilon} \right)^{1/2} - c n t^2 \frac{1}{\sigma^2 (sB)^4} \big)
\]
for all $n > n_0$.

Restating, we have that with probability at most $1- \frac{1}{n}$, the deviation is at most 
\begin{align}
\sqrt{ \frac{1}{cn} \sigma^2 (sB)^4 \left( \log Cn + s( \frac{bBLs}{\epsilon})^{1/2} \right)} \label{eqn:finite_cover_deviation}
\end{align}
Substituting in $\epsilon = \frac{bBLs}{n^{2/5}}$, expression~\ref{eqn:finite_cover_deviation} becomes $\sqrt{ \frac{1}{cn^{4/5}} \sigma^2 s^5 B^4 \log Cn}$.

Expressions~\ref{eqn:approx_deviation1} and \ref{eqn:approx_deviation2} become $\sqrt{ \frac{(bBLs)^2}{cn^{4/5}}} (B+\sigma)$.

>>>>

Suppose that $c s L \lambda_n \rightarrow 0$ and $c L b (sB+\sigma)sB \sqrt{\frac{s}{n^{4/5}} \log sn} \rightarrow 0$.

@@

By Theorem~\ref{thm:uniform_risk_deviation}, we know that under the condition of the theorem, $\tau_n \leq  Lb (sB+\sigma) sB \sqrt{ \frac{s}{cn^{4/5}} \log n}$.

@@

For $n$ large enough such that
\[
c s L \lambda_n < \frac{\alpha}{2} \trm{ and } Lb sB (sB+\sigma) \sqrt{ \frac{s}{n^{4/5}} \log sn}) < \frac{\alpha}{4}
\]
we get that $\hat{R}_s(\hat{f}) + \lambda_n \rho_n(\hat{r}) > \hat{R}_s(f^*_s) + \lambda_n \rho_n(f^*_s)$, which is a contradiction since we assumed that $\hat{f}$ minimizes the regularized empirical risk.

@@

\begin{theorem} (Uniform Risk Deviation)
\label{thm:uniform_risk_deviation}
For all $n > n_0$, we have that, with probability at least $1 - \frac{C}{n}$, 
\[
\sup_{f \in \mathcal{C}^s[b,B,L]} |\hat{R}_s(f) - R_s(f)| \leq Lb(sB+\sigma)sB\sqrt{ \frac{s}{cn^{4/5}} \log sn}
\]
\end{theorem}

@@

The first term, fully expanded, is $\frac{1}{n} \sum_{i=1}^n w_i (f_0(X^{(i)}) - \bar{f}_0 - f'(X^{(i)}))$. Since $w_i$ and $X^{(i)}$ are independent, we use the sub-Gaussian concentration inequality. Note that $|f_0(X^{(i)}) - \bar{f}_0 - f'(X^{(i)})| \leq 3sB$, and so $|\langle w, f_0 - \bar{f}_0 - f' \rangle_n | > t$ with probability at most $C \exp\big( - c n t^2 \frac{1}{\sigma^2 (sB)^2} \big)$.

@@

$\bar{w} \leq \sigma\sqrt{\frac{1}{cn}}$ with probability at least $1-\frac{C}{n}$. Thus, $| \bar{w}|^2 \leq \sigma^2 \frac{1}{cn}$ with high probability, has a second order effect, and can be safely ignored in the bound.

@@

\begin{align*}
\| f_0 - \bar{f}_0 - f'\|_n^2 &= \|f_0 -\mu+\mu - \bar{f}_0 - f'\|_n^2 \\
      &= \| f_0 - \mu - f'\|_n^2 + 2 \langle \mu-\bar{f}_0, f_0 - \mu - f'\rangle_n 
          + \|\mu - \bar{f}_0 \|_n^2 
\end{align*}

Using similar reasoning as before, we know that $| \langle \mu-\bar{f}_0, f_0 - \mu - f'\rangle_n | \geq t $ with probability at most $C \exp( - c n t^2 \frac{1}{(sB)^4})$.

Likewise, $| \mu - \bar{f}_0 | \leq sB \sqrt{\frac{1}{cn}}$ with probability at least $1-\frac{C}{n}$. Thus, $| \mu - \bar{f}_0 |^2 \leq (sB)^2 \frac{1}{cn}$, has a second order effect, and can be safely ignored in the bound.

Because $f_0(X^{(i)}) -\mu - f'^(X^{(i)})$ is bounded by $3sB$, $\| f_0 -\mu- f'\|_n^2$ is the empirical average of $n$ random variables bounded by $9(sB)^2$.

Using Hoeffding Inequality then, we know that the probability $\Big| \| f_0 -\mu - f' \|_n^2 - \E(f_0(X) -\mu - f '(X))^2 \Big| \geq t $ is at most $C \exp( - c n t^2 \frac{1}{(sB)^4})$.

Applying union bound, we have that $\sup_{f' \in \mathcal{C}_\epsilon[s,b,B,L]} | \hat{R}_s(f') - R_s(f') | \geq t$ occurs with probability at most
\[
C \exp\big( s\left( \frac{bBLs}{\epsilon} \right)^{1/2} - c n t^2 \frac{1}{\sigma^2(sB)^2 + (sB)^4} \big)
\]
for all $n > n_0$.

Restating, we have that with probability at most $1- \frac{1}{n}$, the deviation is at most 
\begin{align}
(sB+\sigma)sB\sqrt{ \frac{1}{cn} \left( \log Cn + s( \frac{bBLs}{\epsilon})^{1/2} \right)} \label{eqn:finite_cover_deviation}
\end{align}
Substituting in $\epsilon = \frac{bBLs}{n^{2/5}}$, expression~\ref{eqn:finite_cover_deviation} can be upper bounded by $sB(\sigma+sB)\sqrt{ \frac{s}{cn^{4/5}} \log Cn}$.

Expressions~\ref{eqn:approx_deviation1} and \ref{eqn:approx_deviation2} from \textbf{Step 1} and \textbf{Step 2} become $\sqrt{ \frac{(bBLs)^2}{cn^{4/5}}} (sB+\sigma)$.

We can arrive at the statement of the theorem by summing these up and absorbing any constants into the symbols $c$ and $C$.
